---
title: "SGPdata 1.0-0.0"
---

```{r include = FALSE}
    library(SGPdata)

    is_html_output = function() {
        knitr::opts_knit$get("rmarkdown.pandoc.to")=="html"
    }

    knitr::opts_chunk$set(
        collapse=TRUE,
        comment="",
        prompt=TRUE,
        fig.dpi=96)

    if (is_html_output()) {
        options(width=1000)
    }
```


This is the initial release of the **SGPdata** package. The **SGPdata** package supports the [SGP](https://sgp.io) package by providing users with
exemplar data sets to assist user in preparing their data for SGP analyses.

The initial release contains two exemplar data sets: `sgpData` and `sgpData_LONG`.

The data set `sgpData` is an anonymized, panel data set comprisong 5 years of annual assessment data in WIDE format. This exemplar data set specifies the format
for data used with the lower level [`studentGrowthPercentiles`](https://sgp.io/reference/studentGrowthPercentiles.html) and
[`studentGrowthProjections`](https://sgp.io/reference/studentGrowthProjections.html) functions.

```{r}
head(sgpData)
```

The data set `sgpData_LONG` is an anonymized, panel data set comprisong 5 years of annual assessment data in LONG format. This exemplar data set specifies the
format for data used with the higher level functions [`abcSGP`](https://sgp.io/reference/abcSGP.html), [`prepareSGP`](https://sgp.io/reference/prepareSGP.html),
[`analyzeSGP`](https://sgp.io/reference/analyzeSGP.html), [`combineSGP`](https://sgp.io/reference/combineSGP.html), [`summarizeSGP`](https://sgp.io/reference/summarizeSGP.html),
[`visualizeSGP`](https://sgp.io/reference/visualizeSGP.html), and  [`outputSGP`](https://sgp.io/reference/outputSGP.html)

```{r}
head(sgpData_LONG)
```

The LONG data set `sgpData_LONG` also contains other personal information including demographic characteristics. These fields are not used in the
calculation of SGPs but instead for calculating numberous aggregates including school, district, and demographics summaries.

For complete `SGPdata` documentation, see the [getting started vignette](https://CenterForAssessment.github.io/SGPdata/articles/SGPdata.html) and the [documentation](https://CenterForAssessment.github.io/SGPdata/reference/SGPdata.html).
