---
title: "Getting started with SGPdata"
author: "Damian W Betebenner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with SGPdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r include = FALSE}
    library(SGPdata)

    is_html_output = function() {
        knitr::opts_knit$get("rmarkdown.pandoc.to")=="html"
    }

    knitr::opts_chunk$set(
        collapse=TRUE,
        comment="",
        prompt=TRUE,
        fig.dpi=96)

    if (is_html_output()) {
        options(width=1000)
    }
```

# Introduction

The **SGPdata** package contains 4 examplar data set for use with [student growth percentile (SGP)](https://sgp.io) analyses.
One of the data sets, `sgpData`, specifies the proper format for use with the lower level [SGP](https://sgp.io) functions
`studentGrowthPercentiles` and `studentGrowthProjections`.


# WIDE data format: sgpData

The data set `sgpData` is an anonymized, panel data set comprisong 5 years of annual assessment data in WIDE format. This exemplar data set specifies the format
for data used with the lower level [`studentGrowthPercentiles`](https://sgp.io/reference/studentGrowthPercentiles.html) and
[`studentGrowthProjections`](https://sgp.io/reference/studentGrowthProjections.html) functions.

```{r}
head(sgpData)
```

Use of `sgpData` for SGP calculations is covered more extensively in the [SGP Documentation](https://sgp.io). However a simple example illustrates how `sgpData`
is supplied to the `studentGrowthPercentiles` function.

```
> sgp_g4 <- studentGrowthPercentiles(
		panel.data=sgpData,
		sgp.labels=list(my.year=2015, my.subject="Reading"),
		percentile.cuts=c(1,35,65,99),
		grade.progression=c(3,4))
```


# LONG data format: sgpData_LONG

The data set `sgpData_LONG` is an anonymized, panel data set comprisong 5 years of annual assessment data in LONG format. This exemplar data set specifies the
format for data used with the higher level functions [`abcSGP`](https://sgp.io/reference/abcSGP.html), [`prepareSGP`](https://sgp.io/reference/prepareSGP.html),
[`analyzeSGP`](https://sgp.io/reference/analyzeSGP.html), [`combineSGP`](https://sgp.io/reference/combineSGP.html), [`summarizeSGP`](https://sgp.io/reference/summarizeSGP.html),
[`visualizeSGP`](https://sgp.io/reference/visualizeSGP.html), and  [`outputSGP`](https://sgp.io/reference/outputSGP.html)

```{r}
head(sgpData_LONG)
```

# LONG data format with time: sgptData_LONG

```{r}
head(sgptData_LONG)
```

# LONG teacher-student lookup: sgpData_INSTRUCTOR_NUMBER

```{r}
head(sgpData_INSTRUCTOR_NUMBER)
```



# Contributions & Requests

If you have contribution or a feature request for the **SGPdata** package, don't hesitate to write or set up an [issue on GitHub](https://github.com/CenterForAssessment/SGPdata/issues).
