---
title: "Getting started with SGPdata"
author: "Damian W Betebenner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with SGPdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r include = FALSE}
library(SGPdata)
is_html_output = function() {
  knitr::opts_knit$get("rmarkdown.pandoc.to")=="html"
}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "",
    prompt=TRUE,
    fig.dpi = 96
			)
if (is_html_output()) {
    options(width=1000)
}
```

# Introduction

The **SGPdata** package contains 4 examplar data set for use with [student growth percentile (SGP)](https://sgp.io) analyses.
One of the data sets, `sgpData`, specifies the proper format for use with the lower level [SGP](https://sgp.io) functions
`studentGrowthPercentiles` and `studentGrowthProjections`.


# WIDE data format

```{r}
head(sgpData)
```


# LONG data format


```{r}
head(sgpData_LONG)
```

## Basic SGP Examples

The first argument, `n`, controls the number of names returned by the **SGPdata** function:

```{r}
head(sgpData)
```



# Contributions & Requests

If you have contribution or a feature request for the **SGPdata** package, don't hesitate to write or set up an [issue on GitHub](https://github.com/CenterForAssessment/SGPdata/issues).
